draft

### 2025-06-30 draft.tex
fix(draft): — -> --

Alternative tools can extract features for image-based profiles, such as scikit-image \citep{waltScikitimageImageProcessing2014}, ScaleFex, or SpaCR \citep{comoletHighlyEfficientScalable2024,einarolafssonSpaCr2025}, however, these approaches present trade-offs for different use cases. Their independent implementation means they generate different feature sets than CellProfiler, which can be advantageous for novel
 applications but complicates direct comparison with established datasets like those in the Cell Painting Gallery \cite{weisbartCellPaintingGallery2024}. 
Additionally, while all tools necessarily impose input requirements, some enforce rigid organizational constraints—demanding specific directory structures and naming conventions—that require extensive data reorganization before analysis, beyond the standard data type and format specifications.
Some alternatives also target specific deployment scenarios, with ScaleFex designed primarily for cloud environments, limiting utility for researchers preferring local computation.

>>>>

Alternative tools can extract features for image-based profiles, such as scikit-image \citep{waltScikitimageImageProcessing2014}, ScaleFex, or SpaCR \citep{comoletHighlyEfficientScalable2024,einarolafssonSpaCr2025}, however, these approaches present trade-offs for different use cases. Their independent implementation means they generate different feature sets than CellProfiler, which can be advantageous for novel
 applications but complicates direct comparison with established datasets like those in the Cell Painting Gallery \cite{weisbartCellPaintingGallery2024}. 
Additionally, while all tools necessarily impose input requirements, some enforce rigid organizational constraints--demanding specific directory structures and naming conventions--that require extensive data reorganization before analysis, beyond the standard data type and format specifications.
Some alternatives also target specific deployment scenarios, with ScaleFex designed primarily for cloud environments, limiting utility for researchers preferring local computation.
